The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-23 ms.Rmd
Add chunk names.

```{r, echo = FALSE, fig.height = 9, fig.cap = "The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\\label{fig:workflows}"}

@@

```{r, eval = FALSE}
Bioclim <- function (extent = c(-180, 180, -90, 90),
                     resolution = 10,
                     layers = 1:19) {

@@

```{r, eval = TRUE, echo = FALSE, cache = FALSE}
# Keep cache = FALSE. Not supposed to cache chunks with library()
#  I assume we want this not echoed.
library(zoon)

@@

```{r, eval = TRUE}
Feng_Papes <- workflow(occurrence = SpOcc('Dasypus novemcinctus',
                                          extent = c(-130, -20, -60, 60)),
                        covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                            layers = c(1:4, 6, 9, 10, 12, 15)),
                          process = Chain(Clean, # Remove rows w/ impossible, unlikely or missing lat lon.
                                          Background(n = 1000, bias = 200), #background w/in 200km of occurrences
                                          # MESSMask),  # Still to be implemented. mask out areas beyond extremes in train data
                                          Crossvalidate(k = 5)),
                            model = MaxEnt,
                           output = Chain(PerformanceMeasures, PrintMap))

@@

```{r, eval = FALSE}
Feng_Papes_interactive <- ReRunWorkflow(
    Feng_Papes,
    output = Chain(PrintMap, InteractiveMap, ResponseCurve))
```

@@

```{r, eval = FALSE}
CarolinaWrenPO <- function() {

@@

```{r, eval = FALSE}
merow_and_silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = ...,
    process = ...,
    model = list(MaxEnt, MaxLike),
    output = ...)
```

@@

```{r, eval = FALSE}
merow_and_silander_spatial <- ReRunWorkflow(
    merow_and_silander,
    process = Chain(..., PartitionDisc))
```

>>>>

```{r plotzoonoverview, echo = FALSE, fig.height = 9, fig.cap = "The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\\label{fig:workflows}"}

@@

```{r bioclimmodule, eval = FALSE}
Bioclim <- function (extent = c(-180, 180, -90, 90),
                     resolution = 10,
                     layers = 1:19) {

@@

```{r loadzoon, eval = TRUE, echo = FALSE, cache = FALSE}
# Keep cache = FALSE. Not supposed to cache chunks with library()
#  I assume we want this not echoed.
library(zoon)

@@

```{r fengworkflow, eval = TRUE}
Feng_Papes <- workflow(occurrence = SpOcc('Dasypus novemcinctus',
                                          extent = c(-130, -20, -60, 60)),
                        covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                            layers = c(1:4, 6, 9, 10, 12, 15)),
                          process = Chain(Clean, # Remove rows w/ impossible, unlikely or missing lat lon.
                                          Background(n = 1000, bias = 200), #background w/in 200km of occurrences
                                          # MESSMask),  # Still to be implemented. mask out areas beyond extremes in train data
                                          Crossvalidate(k = 5)),
                            model = MaxEnt,
                           output = Chain(PerformanceMeasures, PrintMap))

@@

```{r fengChangeWorkflow, eval = FALSE}
Feng_Papes_interactive <- ChangeWorkflow(
    Feng_Papes,
    output = Chain(PrintMap, InteractiveMap, ResponseCurve))
```

@@

```{r carolinamodule, eval = FALSE}
CarolinaWrenPO <- function() {

@@

```{r merowworkflow, eval = FALSE}
merow_and_silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = ...,
    process = ...,
    model = list(MaxEnt, MaxLike),
    output = ...)
```

@@

```{r mewoChangeWorkflow, eval = FALSE}
merow_and_silander_spatial <- ChangeWorkflow(
    merow_and_silander,
    process = Chain(..., PartitionDisc))
```
